---
title: "Week-2 ODD 2018 April Data Analysis"
author: "Ömer Bayır"
date: "20 Ekim 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## ODD 2018 April Data Analaysis
In week-2 home work we had ODD sales data in Excel. After removing header and footer columns in excel, 
you can load the data in your R worksapce via the code below 

```{r cars}
#install.packages("tidyverse", repos = "https://cran.r-project.org") ##if installed it is not essential
# Load the package to the session
library(tidyverse)
library(readxl)
raw_data <- read_excel("201804.xlsx", col_names = FALSE) ## my excel file name is 201804.xlsx
                                                         ## also you should check your working directory


```
We required to name our data columns with standardised names. Also if we have NA cells we replaced with them 0 or '.' .
My RDS file is ready and  waiting to be merged by merger classmate. 
As seen below :

```{r cars2}
colnames(raw_data) <- c("brand_name","auto_dom","auto_imp","auto_total","comm_dom","comm_imp","comm_total","total_dom","total_imp","total_total")

car_data_april_18 <- raw_data %>% mutate_if(is.numeric,funs(ifelse(is.na(.),0,.))) %>% mutate(year=2018,month=4)

saveRDS(car_data_april_18,file="odd_car_sales_data_april_18.rds")

```
After loading our data frame I've made two analysis. 

```{r cars3}
car_data_april_18 %>%
  tbl_df()



## First Analysis
car_data_april_18 %>% select(year, month, brand_name, total_total) %>% 
  mutate(all_Total=sum(total_total),percentage=total_total/sum(total_total)*100 ) %>%  
    filter(total_total==min(total_total) | total_total==max(total_total))  
```
  
In the first analysis you can see the best performed brand and the worst brands. Their percentage of total sold car in April 2018 can be shown.   

```{r cars4}
## Second Analysis
car_data_april_18 %>% select(year, month, brand_name, total_total) %>% 
  mutate(percentage=total_total/sum(total_total)*100 ) %>%  
  arrange(desc(percentage)) %>% slice(1:10)
```
  
Second analysis shows us total sales brand by brand and their percentage of total sales. The analysis shows only the top ten performer brands.