---
title: "EGM (Pension Monitoring Center) Data Analysis"
author: "Ömer Bayır"
date: "11 Kasım 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## EGM (Pension Monitoring Center) Data Analysis

EGM is responsible monitoring and controlling Pension System in Turkey. EGM shares data about pension system from its website. We have summary data about pension funds, participants and contribution etc. 
We made two analysis and visiulation abaout Avivasa Emeklilik Hayat, which is the leader in the market.

```{r cars}
library(tidyverse)
library(dplyr)
library(readxl)
tmp<-tempfile(fileext=".xlsx")
download.file("https://github.com/MEF-BDA503/pj18-omerbayir/blob/master/week3/egm_example_data.xlsx?raw=true",destfile=tmp,mode = 'wb')
raw_data<-readxl::read_excel(tmp,skip=7,col_names=FALSE)
file.remove(tmp)
head(raw_data)

colnames(raw_data) <- c("date","pension_fund_company","n_of_participants","fund_size_participants","gov_contribution","contribution","n_of_pensioners","n_of_ind_contracts","n_of_group_ind_contracts","n_of_employer_group_certificates","n_total","size_of_ind_contracts","size_of_group_ind_contracts","size_of_employer_group_certificates","size_total")

# Now we replace NA values with 0 and label the time period with year and month, so when we merge the data we won't be confused.
egm_data <- raw_data %>% mutate_if(is.numeric,funs(ifelse(is.na(.),0,.))) 

```



```

## Avivasa's Participants Plot
The line graph below shows Avivasa's participants count day to day depending on the data.

## Pension companies that have higher fund than average
The chart below shows avarage fund for every companies participants. After that elimates the companies that they have   below the market's avarage fund volume.

```{r pressure, echo=FALSE}

egm_data%>%filter(pension_fund_company=="Avivasa Emeklilik ve Hayat") %>% 
  ggplot(data=. , aes(x = 1:nrow(.),y = n_of_participants)) + geom_line() + labs(x = "Day Number", y="Participants")

egm_data %>% mutate(all_fund_avg = mean(fund_size_participants)) %>%
  group_by(pension_fund_company,all_fund_avg) %>% 
  summarise( x=mean(fund_size_participants)  )  %>%
  
select(pension_fund_company,all_fund_avg,x) %>% 
  filter(all_fund_avg<x) %>%
  ggplot(data = ., aes(x = pension_fund_company, y = x, fill = pension_fund_company)) + geom_bar(stat = "identity")+ ylab("Number of Distinct Customers")  + xlab("Companies") 



```
